### 2025-12-08 review/response/letter.tex

First of all, thank you for considering our article "Variational data assimilation for the wave equation in heterogeneous media: Numerical investigation of stability" for publication in \textit{Communications on Applied Mathematics and Computation}. We also thank the reviewers for their valuable comments and suggestions for improvement. Below, we address their points one after another. \\

%------------------------------------------------------------------------------------------------
%------------------------------------------------------------------------------------------------

%------------------------------------------------------------------------------------------------
%------------------------------------------------------------------------------------------------
\subsection*{Referee 1}	
%------------------------------------------------------------------------------------------------
%------------------------------------------------------------------------------------

\begin{enumerate}
  \item \emph{The Geometric Control Condition (GCC) was originally introduced in [8]. However, the
  manuscript does not clarify how GCC satisfaction is verified in the specific numerical
  simulations. For completeness, I recommend including a precise definition of the GCC.}
  \reply{\textbf{add a bit of detail, lightlike..., precise definition to technical...} @Janosch}
  \item \emph{On page 7, could the authors clarify whether $\bm{Z}_h$ belongs to the space $\mathcal{W}_{h, \Delta t}^{k^{\ast},q^{\ast}}$?}
  \reply{Indeed, it does belong to $\mathcal{W}_{h, \Delta t}^{k^{\ast},q^{\ast}}$. We have added this after the definition of the Lagrangian $\mathcal{L}$.}
  \item \emph{In the numerical experiments, what values are chosen for the parameters $k, q, k^{\ast}$ and
  $q^{\ast}$? The current description appears to only specify the value of $k$.}
  \reply{We have added the values of $q, k^{\ast}, q^{\ast}$ for the numerical experiments. \textbf{@ Janosch, why do we choose them that way?}}
  \item \emph{How is the “best approximation” determined in the numerical experiments? Please explain the criteria or method used to obtain it.}
  \reply{In the numerical experiments, we compare the approximation error of our method with the $L^2$-best approximation error, i.e. we calculate the $L^2$-orthogonal projection of the exact solution onto the discrete space. We have added a footnote.}
  \item \emph{On page 18, the black line in Figure 5, does it represent the exact solution at time 0.5
  or at time 1? It seems to depict the solution at $T = 1.0$, where the approximation
  matches the exact solution well. The exact solution at $T = 0.5$ does not appear to be shown.}
  \reply{We compute the approximation twice, once with final time $T = 0.5$ and once with final time $T = 1.0$, but compare it for both cases at $t = 0.5$. The figure illustrates that the approximation is not reliable if the final time is not large enough to satisfy the GCC. We have slightly adjusted the text and the figure to avoid any misunderstandings.}
  \item \emph{In the two-dimensional case, only a square data domain is considered. A more interesting scenario would involve a curved interface, such as a circular interface. Could the
  authors provide related numerical results for such a case?}
\end{enumerate}

\subsection*{Referee {2}}	
%------------------------------------------------------------------------------------------------
%------------------------------------------------------------------------------------------------
\begin{enumerate}
  \item \emph{How did you numerically verify Assumption 1? Specifically, how were the two
  inequalities in Assumption 1 verified?}
  \reply{We do not verify Assumption 1 numerically. The takeaway from the analysis presented in the article is that we expect our numerical method to exhibit the same stability as the continuous problem. Therefore, we check whether the assumption of the GCC grants good convergence rates. We refer to the last paragraphs of the introduction and also Remark 2.}
  \item \emph{What is the relationship between the GCC and condition (1.3)? In the numerical tests in Section 4.1, you use condition (1.3) to imply the GCC. It appears that you have verified stability under a much stronger condition. I am wondering what would happen if you directly let the data satisfy the GCC, as you did in Section 4.2. Moreover, could you please explain why $T = 0.75$ was chosen in
  Section 4.2? Would a smaller $T$ work?}
  \reply{In general, the GCC is a stronger assumption than (1.3), because (1.3) only grants unique solvability, but stability can be (very) poor. The GCC ensures better stability. In the 1D case, however, both conditions are equivalent ((1.3) implies the GCC in 1D) and thus, we can focus on (1.3) for the 1D experiments. We have added a sentence in the article to point that out.}
  \reply{\textbf{2D not sure, think about this after modifications from Ref 1}}
  \item \emph{Could you please explain why you adopted the discontinuous-in-time FEM
  method? What are the advantages of this method for the problem under consideration?}
  \reply{@ Janosch}
  \item \emph{Please clarify the choices of $q$, $k^{\ast}$ , and $q^{\ast}$ in the numerical experiments.}
  \reply{We have added the values of $q, k^{\ast}, q^{\ast}$ for the numerical experiments.}
  \item \emph{Please clarify the conditions of Lemma 3.1. Does it require the GCC or condition
  (1.3)?}
  \reply{It requires (1.3), which is required for unique solvability anyway. We have added a short sentence in the beginning of Sec. 3.1 that we assume (1.3) to be satisfied.}
  \item \emph{The authors are encouraged to provide a detailed proof of Lemma 3.3.}
  \reply{We added a proof of Lemma 3.3.} 
  \item \emph{What would happen if $c_1$ becomes larger?}
  \reply{We observe that the larger the contrast, the harder the problem is to resolve numerically. We point that out in the conclusion and the discussion in Section 4.2. The conclusion that the GCC seems to imply Lipschitz stability does not change for higher contrasts.}
  \item \emph{Please clarify the meaning of “the $L^2$ -best approximation errors” in the numerical section.}
  \reply{We have added a footnote (see above, point 4.).}
  \item \emph{Typo: last line on page 19, “$L^2$ -bestapproximation” $\to$ “$L^2$ -best approximation”.}
  \reply{We thank the review for spotting this typo. We have corrected it.}
\end{enumerate}
